### 2020-01-21 introduction.tex
more intro

Differential testing \cite{McKeeman,ICSEDiff} is a popular approach to comparing multiple software systems offering similar functionality, but the wide divergence of possible trade-offs, analysis focuses, and the prevalence of false positives in almost all analysis results makes na\"ive differential testing not applicable to static analysis tools \cite{regehrRandom}.

>>>>

Differential testing \cite{Differential,ICSEDiff} is a popular approach to comparing multiple software systems offering similar functionality, but the wide divergence of possible trade-offs, analysis focuses, and the prevalence of false positives in almost all analysis results makes na\"ive differential testing not applicable to static analysis tools \cite{regehrRandom}.
